Understanding domestic abuse - Pathways to Impact

### 2019-07-26 pathways_to_impact.tex
N minor edits to pathways to impact

Our pathway to impact is built upon the strong existing relationships we have with Wast Midlands Police (WMP), and the College of Policing (CoP). These existing relationships are complemented by our membership of the University of Warwick's Centre for Operational Policing Research (COPR), which provides access to an even wider established network within UK policing.

The research proposed here has been developed with direct input from officers and experts within WMP. This has allowed us to design the research questions that are relevant to current issues within the WMP, and that can feed in to existing structures to accelerate the dissemination of findings, and contribute to changes in policy. To facilitate this, we have a day-to-day contact at WMP with Inspector Jenny Richards (Evidence Based Practice in Risk and Organisational Learning), and Alison Spence (Crime Commissioner's Office). As a result of this close collaboration, we have received support from senior levels within WMP including from Deputy Chief Constable Louisa Rolfe, who is the National Police Chiefs Council lead for domestic abuse.

These relationships will enable us to work with WMP to import insights generated from our the research into their senior management team, and also their day-to-day processes. This will be possible for each of the objectives and topics within our proposal:

@@

2. The programme on the  ``decision to report'' links with police's design of the initial contact with victims (e.g., https://west-midlands.police.uk/your-options/domestic-abuse). It will also help the police to develop more efficient and targeted intervention and awareness campaigns.

@@

In the second year of the proposal, we will hold a 1-day impact summit at Warwick Business School's London Shard venue. This will be funded by the Warwick Business School Impact Fund, and potentially the ESRC Impact Acceleration Account. We will host the National Police Chiefs' Council lead for Domestic Abuse, Deputy Chief Constable Louisa Rolfe (who is also at WMP), and Members of Parliament from the Home Affairs Committee domestic abuse inquiry. The summit will be a 50/50 academic and practitioner mix. We will contact, early in the project, domestic abuse charities including Women's Aid, Refuge, Safe Lives, and National Centre for Domestic Abuse, and visit them at their offices to present the programme of research and involve them as we conduct the initial analysis.

@@

Although a high-profile dissemination event at the Shard will attract attention, it is the continuous week-on-week contact with our impact partners that we think will deliver the legacy impact for this project.

@@

We will apply to the Warwick ESRC Impact Acceleration Account and to Warwick Business School Impact Fund to continue the impact programme beyond the end of the funded period.

>>>>

Our pathway to impact is built upon the strong existing relationships we have with West Midlands Police (WMP), and the College of Policing (CoP). These existing relationships are complemented by our membership of the University of Warwick's Centre for Operational Policing Research (COPR), which provides access to an even wider established network within UK policing.

The research proposed here has been developed with direct input from officers and experts within WMP. This has allowed us to design the research questions that are relevant to current issues within the WMP, and that can feed in to existing structures to accelerate the dissemination of findings, and contribute to changes in policy. To facilitate this, we have a day-to-day contact at WMP with Inspector Jenny Richards (Evidence Based Practice in Risk and Organisational Learning), and Alison Spence (Crime Commissioner's Office). As a result of this close collaboration, we have received support from senior levels within WMP including from Deputy Chief Constable Louisa Rolfe, who is the National Police Chiefs' Council lead for domestic abuse.

These relationships will enable us to work with WMP to import insights generated from our the research into their senior management team and ultimately to influence policy and day-to-day operations. This will be possible for each of the objectives and topics within our proposal:

@@

2. The programme on the  ``decision to report'' links with police's design of the initial contact with victims (e.g., \url{https://west-midlands.police.uk/your-options/domestic-abuse}). It will also help the police to develop more efficient and targeted intervention and awareness campaigns.

@@

We will contact, in the first three months of project, domestic abuse charities including Women's Aid, Refuge, Safe Lives, and National Centre for Domestic Abuse, and visit them at their offices to present the programme of research and involve them as we conduct the initial analysis.

In the second year of the proposal, we will hold a 1-day impact summit at Warwick Business School's London Shard venue. This will be funded by the Warwick Business School Impact Fund, and potentially the ESRC Impact Acceleration Account. We will host the National Police Chiefs' Council lead for Domestic Abuse, Deputy Chief Constable Louisa Rolfe (who is also at WMP), and Members of Parliament from the Home Affairs Committee domestic abuse inquiry, and key contacts from the third sector agencies. The summit will be a 50/50 academic and practitioner mix. Although a high-profile dissemination event at the Shard will attract attention, it is the continuous week-on-week contact with our impact partners that we think will deliver the legacy impact for this project.

@@

@@

We will apply to the Warwick ESRC Impact Acceleration Account and to Warwick Business School Impact Fund and continue the impact programme beyond the end of the funded period.
